
% Last updated September 19, 2021

\documentclass[11pt]{letter}

\long\def\omit#1{\relax}

\usepackage{
  amssymb, % \checkmark
  enumerate,
  fullpage,
  ifthen,
  multicol,
  palatino,
  url
}

\usepackage[
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue,
  anchorcolor=blue]{hyperref}

\newboolean{AllInstitutionsBoolean}
\setboolean{AllInstitutionsBoolean}{true}
\newcommand{\IfAllInstitutions}[1]{
  \ifthenelse{\boolean{AllInstitutionsBoolean}}{#1}{}
}
  
\newcommand{\ck}{\checkmark}

\newcommand{\comment}[1]{}

\begin{document}

\newcommand{\heading}[1]{ \vspace{11pt} {\Large #1} \\ \rule{6.5in}{.5pt} }

{\Large Kevin A. Wortman}
\begin{multicols}{2}
Department of Computer Science\\
California State University, Fullerton\\
800 N. State College Blvd.\\
Fullerton, CA 92831\\

Email: kwortman@fullerton.edu\\
Office: CS-536\\
Phone: 657-278-2968\\
\end{multicols}

\heading{Education}

\textbf{University of California, Irvine,} Ph.D., Information and Computer Science, 2009 \\
\emph{Advisor:} David Eppstein

\textbf{University of California, Irvine,} M.S., Information and Computer Science, 2004 \\
\emph{Concentration:} Algorithms and Data Structures

\textbf{University of Massachusetts, Amherst,} B.S., \emph{cum laude}, 2002\\
\emph{Majors:} Computer Science, Mathematics

\heading{Academic Employment}

\textbf{Professor,} Department of Computer Science, CSU Fullerton, 2022 -- present

\IfAllInstitutions{
\textbf{Visiting Associate Professor,} MCS Program, Department of Computer Science, UC Irvine, Winter 2022, Spring 2020 and Spring 2019
}

\textbf{Associate Professor,} Department of Computer Science, CSU Fullerton, 2015 -- 2022

\textbf{Assistant Professor,} Department of Computer Science, CSU Fullerton, 2009 -- 2015

\textbf{Research Assistant,} Department of Computer Science, UC Irvine, under David Eppstein, Fall 2008

\textbf{Teaching Assistant,} Donald Bren School of Info. and Computer Sciences, UC Irvine,  2003--2005

\textbf{Summer Research Staff,} MIT Lincoln Laboratory, Lexington, Massachusetts, Summer 2002

\textbf{Undergraduate Research Assistant,} Laboratory for Advanced Software Engineering Research, Amherst, Massachusetts, June 2000 to December 2001

\heading{Industry Employment}

\textbf{Engineering Co-Op,} Unisys, Mission Viejo, California, 2008--2009 %July 2008 to August 2009

\textbf{Engineering Intern,} Google, Mountain View, California, 2005--2007 % June to August 2005; January 2006 to August 2007

\textbf{Intern,} Tektronix, Chelmsford, Massachusetts, 1997--1999 %summers of 1997, 1998, and 1999

\clearpage
\heading{Publications}

\renewcommand{\labelenumi}{I-\arabic{enumi}.}
\textbf{Invited Journal Articles (peer reviewed)}
\begin{enumerate}
\item \label{item:awfn_journal} J. Augustine, D. Eppstein and K. A. Wortman, \emph{Approximate Weighted Farthest Neighbors and Minimum Dilation Stars,} Discrete Mathematics, Algorithms and Applications (DMAA), v. 2, i. 4, pp. 553-565, DOI: 10.1142/S17938309100008872010, 2010.  Preliminary version listed as C-\ref{item:awfn_conference}.
\item \label{item:mds_journal} D. Eppstein and K. A. Wortman, \emph{Minimum Dilation Stars,} Computational Geometry: Theory and Applications, v. 37, i. 1, pp. 27-37, 2007.  Preliminary version listed as C-\ref{item:mds_conference}.
\end{enumerate}

\renewcommand{\labelenumi}{J-\arabic{enumi}.}
\textbf{Journal Articles (peer reviewed)}
\begin{enumerate}
\item \label{item:oarpdsf_journal} D. Eppstein and K. A. Wortman, \emph{Optimal Angular Resolution for Face-Symmetric Drawings}, J. Graph Algorithms and Applications (JGAA), v. 15, i. 4, pp. 551-564, 2011.
\end{enumerate}

\renewcommand{\labelenumi}{C-\arabic{enumi}.}
\textbf{Conference Proceedings (peer reviewed)}
\begin{enumerate}
\item \label{item:ccwc21smith} K. A. Wortman and Nicholas Smith, \emph{CombinoChord: A Guitar Chord Generator App,} IEEE 11th Annual Computing and Communication Workshop and Conference (CCWC 2021), Las Vegas, Nevada, 2021.
\item \label{item:ccwc21palit} Shekhar Palit and K. A. Wortman, \emph{Perfect Tabular Hashing in Pseudolinear Time,} IEEE 11th Annual Computing and Communication Workshop and Conference (CCWC 2021), Las Vegas, Nevada, 2021.
\item \label{item:ccwc20} Coleman Nugent and K. A. Wortman, \emph{Crumple Trees,} IEEE 10th Annual Computing and Communication Workshop and Conference (CCWC 2020), Las Vegas, Nevada, 2020.
\item \label{item:its14} J.R. Richardson and K. A. Wortman, \emph{Street Scanner Geo-Location,} 21st Intelligent Transport Systems World Congress (IST 2014), Detroit, Michigan, 2014.
\item \label{item:isbra13} P. Danaee, K. A. Wortman, S. X. Wang, \emph{Pseudoknotted RNA Secondary Structure Detection Using Artificial Neural Network,} 9th International Symposium on Bioinformatics Research and Applications (ISBRA 2013), Charlotte, North Carolina, 2013.
\item \label{item:cccg12} J. M. White and K. A. Wortman, \emph{Divide-and-Conquer 3D Convex Hulls on the GPU,} 24th Canadian Conference on Computational Geometry (CCCG 2012), Prince Edward Island, Canada, 2012, pp. 137-142.
\item \label{item:awfn_conference} J. Augustine, D. Eppstein and K. A. Wortman, \emph{Approximate Weighted Farthest Neighbors and Minimum Dilation Stars}, 16th International Computing and Combinatorics Conference (COCOON 2010), Nha Trang, Vietnam.  Final version listed as I-\ref{item:awfn_journal}.
\item M. Dickerson, D. Eppstein and K. A. Wortman, \emph{Dilation, Smoothed Distance, and Minimization Diagrams of Convex Functions,} 7th Int. Symp. Voronoi Diagrams in Science and Engineering (ISVD 2010), Quebec City, Canada, pp. 13-22.
\item \label{item:star_metrics} D. Eppstein and K. A. Wortman, \emph{Optimal Embedding Into Star Metrics,} Algorithms and Data Structures Symposium (WADS), Banff, Canada (best paper co-award).  Lecture Notes in Comp. Sci. 5664, 2009, pp. 290-301.
\item \label{item:mds_conference} D. Eppstein and K. A. Wortman, \emph{Minimum Dilation Stars,} ACM Symposium on Computational Geometry (SoCG), Pisa, Italy, 2005, pp. 321-326.  Final version listed as I-\ref{item:mds_journal}.
\end{enumerate}

\renewcommand{\labelenumi}{S-\arabic{enumi}.}
\textbf{Standards Documents (peer reviewed)}
\begin{enumerate}
\item \label{item:srfi134} K. A. Wortman and J. Cowan,
  \emph{SRFI 134: Immutable Deques,}
  Scheme Requests for Implementation, 2016,
  \url{https://srfi.schemers.org/srfi-134/}
\end{enumerate}

\renewcommand{\labelenumi}{P-\arabic{enumi}.}
\textbf{Poster Presentations (peer reviewed)}
\begin{enumerate}
  \item \label{item:hills} K. Torres and K. A. Wortman,
  \emph{The Hills are Designed with the Sound of Music,}
  CSUF ECS Student Projects Showcase and Awards, 2019.
\item \label{item:fmtree} J. Clay and K. A. Wortman, \emph{A Durable Flash Memory Search Tree,} 3rd International Conference on Computational Sustainability (CompSust'12), Copenhagen, Denmark, 2012.
\end{enumerate}

% back to normal numbering
\renewcommand{\labelenumi}{\arabic{enumi}.}

\heading{Teaching}

\textbf{Courses Taught --- CSU Fullerton}

  \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|c|}
  \hline
  \textbf{Term} &
  \textbf{120} &
  \textbf{131} &
  \textbf{223C} &
  \textbf{254} &
  \textbf{305} &
  \textbf{335} &
  \textbf{439} &
  \textbf{452} &
  \textbf{481} &
  \textbf{484} &
  \textbf{535} &
  \textbf{597} \\ \hline

  %            120  131  223C 254  305  335  439  452  481  484  535  597  
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
%              &    &    &    &    &    &    &    &    &    &    &    &    \\ \hline
  Fall   2021 &    &\ck &    &    &    &    &    &    &    &    &\ck &    \\ \hline
  Spring 2021 &    &    &    &    &    &\ck &\ck &    &    &    &    &    \\ \hline
  Fall   2020 &    &\ck &    &    &    &    &    &    &    &    &\ck &    \\ \hline
  Spring 2020 &\ck &    &    &    &    &    &    &    &    &\ck &    &    \\ \hline
  %            120  131  223C 254  305  335  439  452  481  484  535  597  
  Fall   2019 &\ck &    &    &    &    &    &    &    &    &    &\ck &    \\ \hline
  Summer 2019 &    &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Spring 2019 &    &    &    &    &    &\ck &    &    &    &\ck &\ck &    \\ \hline
  Fall   2018 &\ck &    &    &    &\ck &\ck &    &    &    &    &    &    \\ \hline
  Summer 2018 &    &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Spring 2018 &    &    &    &    &    &\ck &    &    &    &\ck &    &    \\ \hline
  Fall   2017 &    &    &    &    &\ck &\ck &    &    &    &    &    &    \\ \hline
  Summer 2017 &    &    &    &    &    &    &    &\ck &    &    &    &    \\ \hline
  % Spring 2017 was sattabical
  Fall   2016 &    &\ck &    &    &    &    &\ck &    &    &    &    &    \\ \hline
  Spring 2016 &    &\ck &    &    &    &    &    &    &    &\ck &    &    \\ \hline
  Fall   2015 &    &\ck &    &    &    &    &\ck &    &    &    &    &    \\ \hline
  Summer 2015 &    &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Spring 2015 &    &    &\ck &    &    &\ck &    &    &    &    &    &    \\ \hline
  Fall   2014 &    &    &    &    &    &\ck &\ck &    &    &    &    &    \\ \hline
  Summer 2014 &    &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Spring 2014 &    &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Fall   2013 &    &\ck &    &    &    &    &    &    &\ck &    &    &    \\ \hline
  Summer 2013 &    &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Spring 2013 &    &\ck &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Fall   2012 &\ck &    &    &    &    &    &    &    &    &    &    &    \\ \hline
  Summer 2012 &    &    &    &    &    &\ck &    &\ck &    &    &    &    \\ \hline
  Spring 2012 &\ck &    &    &    &    &\ck &\ck &    &    &    &    &    \\ \hline
  Fall   2011 &\ck &    &    &    &    &    &    &    &    &    &    &\ck \\ \hline
  Summer 2011 &    &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Spring 2011 &\ck &    &    &\ck &    &\ck &    &    &    &    &    &    \\ \hline
  Fall   2010 &\ck &    &    &    &    &    &    &    &    &    &    &    \\ \hline
  Summer 2010 &    &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  Spring 2010 &\ck &    &    &\ck &    &\ck &    &    &    &    &    &    \\ \hline
  %            120  131  223C 254  305  335  439  452  481  484  535  597  
  Fall   2009 &\ck &    &    &    &    &\ck &    &    &    &    &    &    \\ \hline
  %            120  131  223C 254  305  335  439  452  481  484  535  597  
\end{tabular}
\comment{
\begin{enumerate}
\item CPSC 120 Introduction to Programming: Fall 2019, Fall 2018, Fall 2012,  Spring 2012, Fall 2011, Spring 2011, Fall 2010, Spring 2010, Fall 2009
\item CPSC 131 Data Structures Concepts: Fall 2016, Spring 2016, Fall 2015, Spring 2013, Fall 2013
\item CPSC 223C C Programming: Spring 2015
\item CPSC 254 Unix and Open Source Software: Spring 2011, Spring 2010
\item CPSC 305 Coding for Artists: Fall 2018, Fall 2017
\item CPSC 335 Algorithm Engineering: Summer 2019, Spring 2019, Fall 2018, Summer 2018, Spring 2018, Fall 2017, Summer 2015, Spring 2015, Fall 2014, Summer 2014, Spring 2014, Summer 2013, Spring 2013, Summer 2012, Spring 2012, Summer 2011, Spring 2011, Summer 2010, Spring 2010, Fall 2009
\item CPSC 433 Data Security and Encryption: Summer 2012
\item CPSC 439 Theory of Computation: Fall 2016, Fall 2015, Fall 2014, Spring 2012
\item CPSC 452 Cryptography: Summer 2017, Summer 2012
\item CPSC 481 Artificial Intelligence: Fall 2013
\item CPSC 484 Principles of Computer Graphics: Spring 2019, Spring 2018, Spring 2016
\item CPSC 535 Advanced Algorithms: Fall 2019, Spring 2019
\item CPSC 597 Graduate Project: Fall 2011
\end{enumerate}
}

\IfAllInstitutions{
\textbf{Courses Taught --- UC Irvine}
\begin{itemize}
  \item COMPSCI 261P Data Structures: Winter 2022, Spring 2020, Spring 2019
\end{itemize}
}

\textbf{Courses Developed}
\begin{enumerate}
\item CPSC 535 Advanced Algorithms, first offered Spring 2019
\item CPSC 305 Coding For Artists, first offered Fall 2017
\item CPSC 223C C Programming, first offered Spring 2015
\item CPSC 439 Theory of Computation, first offered Fall 2014
\item CPSC 223P Python Programming, co-proposer, first offered Fall 2012
\end{enumerate}

\textbf{Teaching Assistant Experience --- UC Irvine}
\begin{enumerate}
\item Fall 2005: Honors Intro. to CS I (H21)
\item Spring 2004: Honors Intro. to CS III (H23)
\item Winter 2004: Honors Intro. to CS II (H22)
\item Fall 2003: Formal Languages and Automata (162)
\item Spring 2003: Engineering Data Structures (160E)
\item Winter 2003: Honors Intro. to CS III (H23)
\end{enumerate}

\heading{Advising}

\textbf{Masters Theses Advised}
\begin{enumerate}
\item Mohammed Alfraihi, \emph{Improving the Standard Ant Clustering Algorithm Using Genetic Algorithms}, Fall 2013
\item Hussein Altabrawee, \emph{3D Convex Hull Algorithms in the MapReduce Model (tentative title),} Fall 2013
\item Brian Croner, \emph{Offline Intelligent Lossless Compression of Hyperlinked Documents,} Spring 2012
\item James Clay, \emph{An Efficient Multi-Level Flash Data Structure,} Fall 2011
\item Mihai Marinescu, \emph{Wear-Resistant Flash Hash Tables,} Fall 2011
\item David Luu, \emph{Numerical Methods in Prime Factorization: To Find or not to Find a Prime,} Summer 2010
\end{enumerate}

\textbf{Masters Projects Advised}
\begin{enumerate}
  \item Elizabeth Tsan, \emph{Radically Different,} Fall 2019
  \item Swati Swahoo, \emph{Private Cloud Computing,} Summer 2019
  \item Nishant Rathi, \emph{Code Runner,} Spring 2018
\item Dana Toribio, \emph{Curriculum Graph Visualizer,} Spring 2016
\item Gary Tse, \emph{Graphics Software Tool Plugin based on Skeleton Extraction from a Closed Polygon Mesh,} Spring 2016
\item Colin Poan, \emph{Creating an OLAP Data Warehouse from a Real-World OLTP Database in Order to Increase Data Extract Performance,} Fall 2015
\item Nicholas Smith, \emph{CombinoChord: A Guitar Chord Generator App}, Fall 2015
\item Rodrigo Bryan Gonzalez Sr., \emph{CryptoLock,} Fall 2014
\item John Saxton, \emph{Automated C++ Grading Application,} Spring 2014
\item Yasaman Shahmohammad, \emph{Computational Geometry Algorithms for 3D Printing Applications (tentative title),} Spring 2014
\item Yousef Aloumi, \emph{Arabic Optical Character Recognition Mobile Application,} Fall 2013
\item Toan Nguyen, \emph{Street Scanner Phase 1,} Fall 2013
\item Paul Parker, \emph{Compress Wikipedia: Text Compression Optimizations via the Christophides Approximation Algorithm for the Travelling Salesman Problem,} Spring 2013
\item Leon Smith II, \emph{Medical SMS Expert System,} Spring 2013
\item Brenda Griffith, \emph{A Developer’s Checklist for White Box Testing: A Human Factors Perspective,} Spring 2012
\item Alejandro Alvarenga, \emph{Design and Implementation of a Secure Role Access Control Web Based Healthcare Credentialing Tracking System for the Cal State Fullerton Health Center,} Fall 2011
\item Aseel Ashoor, \emph{C++ Parallel Skip List Implementation,} Fall 2011
\item Brian Badal, \emph{Automated Data Extraction From Remote Database,} Fall 2011
\item Arunkumar Chandrasekaran, \emph{Implement a Dynamic Programming Algorithm for Matrix Chain Multiplication Using MapReduce,} Fall 2011
\item Dena Fitzgerald, \emph{Baby Record iPhone Application,} Fall 2011
\item Christa McCarthy, \emph{Neural Networks as a Blog Comment Spam Filter,} Fall 2011
\item Jaydeep Patel, \emph{Hybrid Classifier: A Clustered Decision Tree,} Fall 2011
\item Bhavana Sudharshan, \emph{A Demonstration of the ``Categorization of Web Documents Using Extraction Ontologies'' Approach for Mobile Phones Application Domain,} Fall 2011
\end{enumerate}

\omit{
\textbf{Masters Theses Reviewed}
\begin{itemize}
\item Tuyet Le, \emph{Single Triangle Strips for Graphs With Boundaries,} Spring 2011
\item Ashish Patel, \emph{Cake Cutting For Real World Problems,} Fall 2010
\item Rachan Tananuchittikul, \emph{Simulating Collisions between Granu’ar Phenomena,} Fall 2010
\end{itemize}

\textbf{Masters Projects Reviewed}
\begin{itemize}
\item Edward Duterte, \emph{Premiere Sports System,} Spring 2011
\item Jochen Schmitt, \emph{Implementation and Analysis of Face Recognition Algorithms,} Spring 2011
\item Aasma Zahid, \emph{Open Source Virtual Folder - Application of Cloud Computing,} Spring 2011
\item Vaishali Saral, \emph{Implementing Multimodal Biometric System,} Fall 2010
\item Krishna Balasa, \emph{Performance Evaluation of TCP Algorithm Suitable for High Bandwidth-Delay Product Network,} Summer 2010
\end{itemize}
}

\heading{Funding}

\textbf{Funded Awards}
\begin{enumerate}
\item \emph{Street Scanner,} Raytheon Company, PI, 2013, \$25,000.
\item \emph{Funding My Research: A Grant Writing Series,} 2012, \$1,000.
\item \emph{Promoting Undergraduate Research Experiences (PURE) Grant Program,} 2011, \$1,000.
\end{enumerate}

\textbf{Unfunded Proposals}
\begin{enumerate}
\item \emph{Enhanced Programming Curriculum for the Retention of Computer Science and Computer Engineering Students,} Association of American Colleges \& Universities, co-PI, 2014.
\item \emph{Ensuring Student Success in Engineering and Computer Science (ESSECS),} National Science Foundation, co-PI, 2012.
\item \emph{Proposal for Development of a CCOS Archive,} Central California Ozone Study, PI, 2011.
\item \emph{Signal and Image Processing,} IEEE Real-World Engineering Projects (RWEP), co-PI, 2010.
\end{enumerate}

\heading{Service}

\textbf{University-Level}
\begin{enumerate}
\item Academic Master Plan Committee: AY 2015-2016
\item General Education Committee: AY 2016-2017, 2015-2016
\item General Education Task Force: AY 2019-2020, 2018-2019, 2017-2018
\item Promoting Undergraduate Research Experiences Committee (PURE): AY 2010-2011
\item SafeSpace Ally, CSU Fullerton Multicultural Leadership Center: 2009-present
\item Supplemental Instruction (SI) Department Liason: AY 2016-2017, 2015-2016, 2014-2015, 2013-2014
%\item Judge, on-campus selection for the CSU System-wide Research Competition: Spring 2012
\end{enumerate}

\textbf{College of Engineering and Computer Science}
\begin{enumerate}
\item Ad-Hoc Committee: AY 2017-2018
\item Commencement Committee: AY 2012-2013, 2011-2012, 2010-2011, 2009-2010
\item Curriculum Committee: AY 2017-2018, 2016-2017, 2015-2016
\end{enumerate}

\textbf{Department of Computer Science}
\begin{enumerate}
  % missing AY 2015-2016
\item ACM Student Chapter Advisor: AY 2014-2015, 2013-2014, 2012-2011, 2011-2012
\item Assessment Committee: AY 2021-2022 (chair), 2020-2021, 2018-2019, 2017-2018
\item Chair Election Committee Chair: AY 2011-2012
\item Graduate Program Committee: AY 2015-2016, 2014-2015
\item Executive Committee: AY 2012-2013, 2010-2011
\item Personnel Committee: AY 2016-2017, 2015-2016
\item Selection (Faculty Search) Committee: AY 2015-2016, 2014-2015, 2013-2014
\item Undergraduate Program Coordinator: AY 2017-2018, 2016-2017, 2015-2016, 2014-2015
\item Undergraduate Program Committee: AY 2021-2022, 2018-2019, 2017-2018, 2016-2017, 2015-2016, 2014-2015, 2013-2014, 2012-2013, 2011-2012, 2010-2011, 2009-2010
\end{enumerate}

\textbf{Workshops and Roundtables}
\begin{enumerate}
\item \emph{Issues in Educating Veteran Engineers: A Multi-Institution Workshop Exploring Best Practices in Educating Veterans,} University of San Diego, June 15, 2010
\item \emph{Department of Defense Roundtable: A Hispanic Engineering, Science, and Technology Week (HESTEC) 2009 Activity,} University of Texas Pan-American, September 29, 2009
\end{enumerate}

\textbf{Media Coverage}
\begin{enumerate}
\item Orange County Register, \href{https://www.ocregister.com/2020/04/16/animation-opens-pathway-for-csuf-computer-science-grad-to-blend-science-and-art/}{Animation opens pathway for CSUF computer science grad to blend science, art}, April 16, 2020
\item Orange County Register, \href{https://www.ocregister.com/2020/04/16/csuf-computer-science-grad-says-her-goal-is-to-make-technology-secure/}{CSUF computer science grad says her goal is to make technology secure}, April 16, 2020
\item Orange County Register, \href{https://www.ocregister.com/2018/12/05/titan-voice-computer-science-student-inspires-next-generation-of-tech-women/}{Titan Voice: Computer science student inspires next generation of tech women,} December 5, 2018
%\item Pearson Higher Education, \href{http://myprogramminglab.com/success-stories/profiles-of-mpl-users.html}{MyProgrammingLab: A Success Story}
\item The Pollak Library Blog, \href{http://libphp2006.fullerton.edu/blogs/news/2010/12/02/dr-wortmans-top-resources-for-trends-in-computer-science/}{Dr. Wortman's top resources for trends in Computer Science,} invited guest post, December 2, 2010
\end{enumerate}

\textbf{Reviewer}, CCWC 2021, CCWC 2020, SIGCSE 2020, 2013 ACM-ICPC North America Qualifier Contest, \emph{Open Data Structures} (textbook), IEEE Transactions on Education

\textbf{External Reviewer}, Scheme R7RS Working Group 2, J. Algorithms, ACM TALG, ISAAC 2008

\omit{
\textbf{Student Workers Union / UAW Local 2865},  Irvine District 3 Steward, April 2003 to October 2007; Statewide Recording Secretary, May 2005 to October 2007
}

\omit{
\emph{Recording Secretary,} May 2005 to October 2007. \\
\emph{Unit Chair (Irvine),} February 2004 - May 2005. \\
\emph{Head Steward (Irvine),} December 2003 - February 2004. \\
\emph{Steward (Irvine District 3),} April 2003 - December 2003. \\
}

\textbf{Associated Graduate Students, UC Irvine},  Council Representative, School of Information and Computer Science, AY 2004-2005 and AY 2006-2007 \omit{Unix Systems Administrator, January 2004 to December 2004}

\heading{Awards}

\textbf{Best Software}, CSUF ECS Student Projects Showcase and Awards, for
  poster P-~\ref{item:hills}, sponsored by Raytheon, 2019

\textbf{Faculty Advisor of Distinction}, CSU Fullerton, March 2018

\textbf{Faculty Recognition: Outstanding Teaching}, CSU Fullerton, March 2014

\textbf{Faculty Recognition: Scholarly \& Creative Activity}, CSU Fullerton, March 2013

\textbf{Outstanding Educator of the Year (College of ECS)}, Associated Students Inc., AY 2012-2013

\textbf{Carol Barnes Excellence in Teaching Award Nominee}, February 2011

\textbf{Faculty Recognition: Scholarly \& Creative Activity}, CSU Fullerton, April 2010

\textbf{Best Paper Award,} Algorithms and Data Structures Symposium (WADS) 2009, for \emph{Optimal embedding into star metrics;} Sponsored by Springer Verlag

\textbf{Graduate Assistance In Areas Of National Need (GAANN) Fellow}, 2004-2005 academic year

\textbf{UMass Amherst Computer Science Talent Advancement Program}, 1998-1999 academic year

\heading{Affiliations}

Association of Computing Machinery (ACM) \\

\heading{Technical Skills}

Programming Languages
\begin{itemize}
\item Expert: C++, LaTeX, Python, Scheme
\item Proficient: C, C\#, Haskell, Java
\item Familiar: BASIC, Bash, Common Lisp, Eiffel, F\#, i386 Assembly, Javascript,
  OpenCL, Reason ML, Rust, Z80 Assembly
\end{itemize}

\end{document}
