
% Last updated October 15, 2024

\documentclass[11pt]{letter}

\long\def\omit#1{\relax}

\usepackage{
  amssymb, % \checkmark
  enumerate,
  fullpage,
  ifthen,
  multicol,
%  palatino,
  url
}

\usepackage[
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue,
  anchorcolor=blue]{hyperref}

\newboolean{AllInstitutionsBoolean}
\setboolean{AllInstitutionsBoolean}{false}
\newcommand{\IfAllInstitutions}[1]{
  \ifthenelse{\boolean{AllInstitutionsBoolean}}{#1}{}
}
  
\newcommand{\ck}{\checkmark}

\newcommand{\comment}[1]{}

\begin{document}

\newcommand{\heading}[1]{ \vspace{11pt} {\Large #1} \\ \rule{6.5in}{.5pt} }

{\Large Kevin A. Wortman}
\begin{multicols}{2}
Department of Computer Science\\
California State University, Fullerton\\
800 N. State College Blvd.\\
Fullerton, CA 92831\\

Email: kwortman@fullerton.edu\\
Office: CS-536\\
Phone: 657-278-2968\\
\end{multicols}

\heading{Education}

\textbf{University of California, Irvine,} Ph.D., Information and Computer Science, 2009 \\
\emph{Advisor:} David Eppstein

\textbf{University of California, Irvine,} M.S., Information and Computer Science, 2004 \\
\emph{Concentration:} Algorithms and Data Structures

\textbf{University of Massachusetts, Amherst,} B.S., \emph{cum laude}, 2002\\
\emph{Majors:} Computer Science, Mathematics

\heading{Academic Employment}

\textbf{Professor,} Department of Computer Science, CSU Fullerton, 2022 -- present

\IfAllInstitutions{
\textbf{Visiting Associate Professor,} MCS Program, Department of Computer Science, UC Irvine, Winter 2022, Spring 2020 and Spring 2019
}

\textbf{Associate Professor,} Department of Computer Science, CSU Fullerton, 2015 -- 2022

\textbf{Assistant Professor,} Department of Computer Science, CSU Fullerton, 2009 -- 2015

\omit{
\textbf{Research Assistant,} Department of Computer Science, UC Irvine, under David Eppstein, Fall 2008

\textbf{Teaching Assistant,} Donald Bren School of Info. and Computer Sciences, UC Irvine,  2003--2005

\textbf{Summer Research Staff,} MIT Lincoln Laboratory, Lexington, Massachusetts, Summer 2002

\textbf{Undergraduate Research Assistant,} Laboratory for Advanced Software Engineering Research, Amherst, Massachusetts, June 2000 to December 2001
}

\omit{
\heading{Industry Employment}

\textbf{Engineering Co-Op,} Unisys, Mission Viejo, California, 2008--2009 %July 2008 to August 2009

\textbf{Engineering Intern,} Google, Mountain View, California, 2005--2007 % June to August 2005; January 2006 to August 2007

\textbf{Intern,} Tektronix, Chelmsford, Massachusetts, 1997--1999 %summers of 1997, 1998, and 1999
}

\heading{Selected Publications}

\begin{enumerate}
  \item \label{item:sigcse24etal} K. A. Wortman, A. Gautam, S. Hug, P. Salvador Inventado, A. M. Kazerouni, J. Lehr, K. Sood, Z. Wood, \emph{Reflecting on Practices to Integrate Socially Responsible Computing in Introductory Computer Science Courses}, ACM Technical Symposium on Computer Science Education (SIGCSE TS) 2025, \emph{accepted}.
  \item \label{item:ccwc21smith} K. A. Wortman and Nicholas Smith, \emph{CombinoChord: A Guitar Chord Generator App,} IEEE 11th Annual Computing and Communication Workshop and Conference (CCWC 2021), Las Vegas, Nevada, 2021.
  \item \label{item:ccwc21palit} Shekhar Palit and K. A. Wortman, \emph{Perfect Tabular Hashing in Pseudolinear Time,} IEEE 11th Annual Computing and Communication Workshop and Conference (CCWC 2021), Las Vegas, Nevada, 2021.
  \item \label{item:ccwc20} Coleman Nugent and K. A. Wortman, \emph{Crumple Trees,} IEEE 10th Annual Computing and Communication Workshop and Conference (CCWC 2020), Las Vegas, Nevada, 2020.
  \item \label{item:its14} J.R. Richardson and K. A. Wortman, \emph{Street Scanner Geo-Location,} 21st Intelligent Transport Systems World Congress (IST 2014), Detroit, Michigan, 2014.
  \item \label{item:isbra13} P. Danaee, K. A. Wortman, S. X. Wang, \emph{Pseudoknotted RNA Secondary Structure Detection Using Artificial Neural Network,} 9th International Symposium on Bioinformatics Research and Applications (ISBRA 2013), Charlotte, North Carolina, 2013.
  \item \label{item:cccg12} J. M. White and K. A. Wortman, \emph{Divide-and-Conquer 3D Convex Hulls on the GPU,} 24th Canadian Conference on Computational Geometry (CCCG 2012), Prince Edward Island, Canada, 2012, pp. 137-142.
  \item \label{item:oarpdsf_journal} D. Eppstein and K. A. Wortman, \emph{Optimal Angular Resolution for Face-Symmetric Drawings}, J. Graph Algorithms and Applications (JGAA), v. 15, i. 4, pp. 551-564, 2011.
  \item \label{item:awfn_journal} J. Augustine, D. Eppstein and K. A. Wortman, \emph{Approximate Weighted Farthest Neighbors and Minimum Dilation Stars,} Discrete Mathematics, Algorithms and Applications (DMAA), v. 2, i. 4, pp. 553-565, DOI: 10.1142/S17938309100008872010, 2010.  Preliminary version listed as C-\ref{item:awfn_conference}.
  \item M. Dickerson, D. Eppstein and K. A. Wortman, \emph{Dilation, Smoothed Distance, and Minimization Diagrams of Convex Functions,} 7th Int. Symp. Voronoi Diagrams in Science and Engineering (ISVD 2010), Quebec City, Canada, pp. 13-22.
  \item \label{item:mds_journal} D. Eppstein and K. A. Wortman, \emph{Minimum Dilation Stars,} Computational Geometry: Theory and Applications, v. 37, i. 1, pp. 27-37, 2007.  Preliminary version listed as C-\ref{item:mds_conference}.
\end{enumerate}

\heading{Teaching}

\textbf{Courses Taught at CSU Fullerton:} CPSC 120, 131, 223C, 254, 305, 335, 439, 452, 481, 484, 533, 535, 597

\textbf{Courses Developed}
\begin{enumerate}
\item CPSC 533 Applied Algorithms, first offered Fall 2024
\item CPSC 535 Advanced Algorithms, first offered Spring 2019
\item CPSC 305 Coding For Artists, first offered Fall 2017
\item CPSC 223C C Programming, first offered Spring 2015
\item CPSC 439 Theory of Computation, first offered Fall 2014
\item CPSC 223P Python Programming, co-proposer, first offered Fall 2012
\end{enumerate}

\heading{Funding}

\begin{enumerate}
\item \emph{Socially Responsible Computing: Promoting Latinx Student Retention Via Community Engagement In Early CS Courses} (NSF BPC), co-PI, \$299,716.
\item \emph{Street Scanner,} Raytheon Company, PI, 2013, \$25,000.
\item \emph{Funding My Research: A Grant Writing Series,} 2012, \$1,000.
\item \emph{Promoting Undergraduate Research Experiences (PURE) Grant Program,} 2011, \$1,000.
\end{enumerate}

\end{document}
